\documentclass{article}

\title{Source-Fidelity Test: Stock article.cls}
\author{legible-pdf}
\date{}

\begin{document}
\maketitle

\section{Heading-One Section}

This paragraph tests basic body text. The next sentence has the word \textit{italic} marked
with \texttt{\textbackslash textit\{\}}, which should render in italic. The phrase
``\emph{emphatic}'' is marked with \texttt{\textbackslash emph\{\}}, which in stock
article.cls also renders italic. The word \textbf{bold} is marked with
\texttt{\textbackslash textbf\{\}}, which should render in bold.

The OpenAI model identifier \texttt{0613} is marked with \texttt{\textbackslash texttt\{\}},
which should render in monospace.

\subsection{Heading-Two Subsection}

This subsection is nested under the section above.

\subsubsection{Heading-Three Subsubsection}

This subsubsection is nested under the subsection above.

\section{Lists}

A bulleted list of three items follows:

\begin{itemize}
    \item First bullet item.
    \item Second bullet item.
    \item Third bullet item.
\end{itemize}

A numbered list of three items follows:

\begin{enumerate}
    \item First numbered item.
    \item Second numbered item.
    \item Third numbered item.
\end{enumerate}

\section{Code Block}

A verbatim block follows:

\begin{verbatim}
def hello(name):
    print(f"Hello, {name}")
\end{verbatim}

\section{Table}

A table with two columns and two data rows follows:

\begin{table}[h]
    \centering
    \begin{tabular}{|l|r|}
        \hline
        \textbf{Model} & \textbf{Accuracy} \\
        \hline
        GPT-3.5-Turbo & 56.1\% \\
        Claude-1.3 & 73.4\% \\
        \hline
    \end{tabular}
    \caption{Sample accuracy table.}
\end{table}

\section{Quote}

A block quote follows:

\begin{quote}
    This is a block quotation. It should render with a left margin offset
    and possibly italic, depending on the class.
\end{quote}

\section{Footnote}

This sentence has a footnote.\footnote{This is the footnote content. It should appear at
the bottom of the page in the rendered PDF.}

\end{document}
